---
title: "Fall 2025 - APJ Capstone "
subtitle: "This is a Report Template Quarto"
author: "Abigail Penza Jackson (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

Slides: [slides.html](slides.html){target="_blank"} ( Go to `slides.qmd`
to edit)

::: callout-important
**Remember:** Your goal is to make your audience understand and care
about your findings. By crafting a compelling story, you can effectively
communicate the value of your data science project.

Carefully read this template since it has instructions and tips to
writing!

Nice report!
:::

## Introduction

The introduction should:

-   Develop a storyline that captures attention and maintains interest.

-   Your audience is your peers

-   Clearly state the problem or question you're addressing.

<!-- -->

-   Introduce why it is relevant needs.

-   Provide an overview of your approach.

Example of writing including citing references:

*This is an introduction to ..... regression, which is a non-parametric
estimator that estimates the conditional expectation of two variables
which is random. The goal of a kernel regression is to discover the
non-linear relationship between two random variables. To discover the
non-linear relationship, kernel estimator or kernel smoothing is the
main method to estimate the curve for non-parametric statistics. In
kernel estimator, weight function is known as kernel function
[@efr2008]. Cite this paper [@bro2014principal]. The GEE [@wang2014].
The PCA [@daffertshofer2004pca]*. Topology can be used in machine learning [@adams2021topology]

For Symbolic Regression [@wang2019symbolic]
*This is my work and I want to add more work...*

Cite new paper [@su2012linear]

## Methods

-   Detail the models or algorithms used.

-   Justify your choices based on the problem and data.

*The common non-parametric regression model is*
$Y_i = m(X_i) + \varepsilon_i$*, where* $Y_i$ *can be defined as the sum
of the regression function value* $m(x)$ *for* $X_i$*. Here* $m(x)$ *is
unknown and* $\varepsilon_i$ *some errors. With the help of this
definition, we can create the estimation for local averaging i.e.*
$m(x)$ *can be estimated with the product of* $Y_i$ *average and* $X_i$
*is near to* $x$*. In other words, this means that we are discovering
the line through the data points with the help of surrounding data
points. The estimation formula is printed below [@R-base]:*

$$
M_n(x) = \sum_{i=1}^{n} W_n (X_i) Y_i  \tag{1}
$$$W_n(x)$ *is the sum of weights that belongs to all real numbers.
Weights are positive numbers and small if* $X_i$ *is far from* $x$*.*


*Another equation:*

$$
y_i = \beta_0 + \beta_1 X_1 +\varepsilon_i
$$

## Analysis and Results

### Data Exploration and Visualization

-   Describe your data sources and collection process.

-   Present initial findings and insights through visualizations.

-   Highlight unexpected patterns or anomalies.

A study was conducted to determine how...

```{r, warning=FALSE, echo=T, message=FALSE}
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
```

```{r, warning=FALSE, echo=TRUE}
# Load Data
kable(head(murders))

ggplot1 = murders %>% ggplot(mapping = aes(x=population/10^6, y=total)) 

  ggplot1 + geom_point(aes(col=region), size = 4) +
  geom_text_repel(aes(label=abb)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(formula = "y~x", method=lm,se = F)+
  xlab("Populations in millions (log10 scale)") + 
  ylab("Total number of murders (log10 scale)") +
  ggtitle("US Gun Murders in 2010") +
  scale_color_discrete(name = "Region")+
      theme_bw()
  

```

### Modeling and Results

-   Explain your data preprocessing and cleaning steps.

-   Present your key findings in a clear and concise manner.

-   Use visuals to support your claims.

-   **Tell a story about what the data reveals.**

```{r}

```

### Conclusion

-   Summarize your key findings.

-   Discuss the implications of your results.

## References

1.	https://journals.sagepub.com/doi/full/10.1177/15501329221106935 

Citation: 
Zhang P, Jia Y, Shang Y. Research and application of XGBoost in imbalanced data. International Journal of Distributed Sensor Networks. 2022;18(6). doi:10.1177/15501329221106935

Summary: This article discusses the limitations of XGBoost when using imbalanced datasets. While the XGBoost is still the primary choice to analyze the data, it is nessassry to automate hyperparameter tuning. In this example that is done with SVM and Bayesian optimization. The sets were evaluated by the G-mean and AUC metrics. The proposed method (mixed sampling + Bayesian-optimized XGBoost) outperformed the traditional usages of XGBoost alone. Public based datasets were used in this example, which is beneficial to our current project. 


2.	https://www.sciencedirect.com/science/article/pii/S2666827021000773

Citation: 
Xin Yu Liew, Nazia Hameed, Jeremie Clos, An investigation of XGBoost-based algorithm for breast cancer classification, Machine Learning with Applications, Volume 6, 2021, 100154, ISSN 2666-8270, https://doi.org/10.1016/j.mlwa.2021.100154. 

Summary: The study conducted research on an enhanced diagnoses tool for breast cancer in women. This was done by “combining Deep Learning and eXtreme Gradient Boosting (XGBoost) to improve histopathological classification for breast cancer diagnosis”. At the time this study was new to machine learning methods by using histology images and not mammograms. The goal, which was accomplished, was to better classify which images showed active cancer and to categorize them into the specific cancer groups. Since the study did accomplish this, further research is being conducted to improve the speed and the accuracy of this methodology. While most of the work and projects I have been apart of in this program, have been datasets, I am very interested in the machine learning of photos and how complex this must be. 

